### 2019-12-12 README.Rmd
new location for csv swap

### Installing from GitHub for use
1. `devtools::install_github("jlucasmckay/msBalance", build_vignettes = TRUE)`
1. `vignette("msBalance")`

>>>>

### Navigating a mixture of Matlab and R code

The source files are in .mat format, using structures like tables and other things that cannot be encoded in the earlier V4-6 .mat file types that can be easily read by R.
There is a mixture of matlab preprocessing code (files in `m/`) into .csv files that R can then read (files in `R/`).
A directory `csv/` is created to hold these files.
The contents of this directory are ignored by git so that these files are not automatically loaded to GitHub, for security purposes.
File path locations need to be

### Installing from GitHub for use

1. `devtools::install_github("jlucasmckay/msBalance", build_vignettes = TRUE)`
1. `vignette("msBalance")`
